### 2021-09-07 input/experiments.tex
cheating on biblio + changes here and there to get to 16 pages
minors

\begin{figure}
  \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_complexity.eps}
  \caption{\label{fig:complexity}Overhead of consistent partitioning
    using \NAME.}

@@

\begin{figure}
  \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_geant.eps}
  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}
\end{figure}

@@

Next Section reviews state-of-the-art approaches for content indexing
in geo-distributed infrastructures and explains their shortcomings.

>>>>

\begin{figure}
  \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_complexity.eps}
  \caption{\label{fig:complexity}Overhead of dynamic consistent partitioning
    using \NAME.}

@@

\begin{figure}
  \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_geant.eps}
  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
\end{figure}

@@

%% Next Section reviews state-of-the-art approaches for content indexing
%% in geo-distributed infrastructures and explains their shortcomings.

### 2021-09-07 input/proposal.tex
minors

\begin{theorem}[\label{theo:threephase}Three-phase purge]
  Purging stale control information from its source to every \process
  that may have delivered it last requires three phases:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possibly blocking conditions, and
  \item propagation of possibly deleted but blocked notifications.
  \end{inparaenum}
\end{theorem}

>>>>

\begin{theorem}[\label{theo:threephase}Three-phase purge]
  The following three phases are sufficient to eventually purge the
  system from stale control information:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possibly blocking conditions, and
  \item propagation of possibly deleted but blocked notifications.
  \end{inparaenum}
\end{theorem}

### 2021-09-07 input/related_work.tex
cheating on biblio + changes here and there to get to 16 pages
minors

\noindent Distance-based membership protocols such as
T-Man~\cite{t-man} make \processes converge to a specific network
topology depending on targeted properties. They periodically
communicate with their neighbors to compare their state. Following
this exchange, they add and remove communication links to other
\processes. Over exchanges, they converge towards a topology ensuring
the targeted properties.  While at first glance membership protocols
and \NAME could share common preoccupations, \NAME does not aim at
building any topology and never modifies neighbors of \processes.

>>>>

\noindent Distance-based membership protocols such as
T-Man~\cite{t-man} make \processes converge to a specific network
topology depending on targeted properties. Following periodic
exchanges, they add and remove communication links to other \processes
to converge towards a topology ensuring the targeted properties.
While membership protocols and \NAME share common preoccupations,
\NAME does not aim at building any topology and never modifies
neighbors of \processes.
